Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2025-03-24 paper/paper.tex
more on nonlinear figures

    \inferrule{\ctxwffjdg \Gamma X}{\ctxwffjdg \Gamma {\listTy{X}}}

@@

\begin{figure}
  \footnotesize
  \begin{mathpar}
    \boxed{\linterm \Gamma \Delta {e} {A}}

@@

\begin{figure}
  \begin{mathpar}
  \footnotesize
    \boxed{\nonlinterm \Gamma M X}

@@

    \inferrule
    {\nonlinterm \Gamma M \bot \and \ctxwffjdg \Gamma X}
    {\nonlinterm \Gamma {elim_{\bot,X}(M)} {X}}

@@

    \inferrule{\ctxwffjdg {\Gamma , b : Bool} {X(b)}}
      {\nonlinterm
        {\Gamma, x_0 : X(false), x_1 : X(true), b : Bool}
        {if\,b\,then\,x_0\,else\,x_1}
        {X(b)}
      }

@@

    \inferrule{~}{\nonlinterm \Gamma {nil} {\listTy{X}}}

    \inferrule
    { \nonlinterm \Gamma {x} {X}
      \and
      \nonlinterm \Gamma {M} {\listTy{X}}}
    {\nonlinterm \Gamma {cons(x,M)} {\listTy{X}}}

    \inferrule
    {
      \ctxwffjdg {\Gamma, xs : \listTy{X}} {Y(xs)} \and
      \nonlinterm {\Gamma} {M} {Y (nil)} \and
      \nonlinterm {\Gamma} {N}
      {\PiTyLimit {x} {X}
        {\PiTyLimit {xs} {\listTy{X}}
          {\PiTyLimit {ys} {Y(xs)} {Y(cons(x,xs))}}}}
    }
    {
      \nonlinterm
      {\Gamma, xs : \listTy{X}}
      {fold(M,N)(xs)}
      {Y(xs)}
    }

@@

\begin{figure}
  \begin{mathpar}
  \boxed{\nonlinterm \Gamma {M \equiv N} {X}}

@@

  \inferrule{\nonlinterm \Gamma M \bot \and \nonlinterm \Gamma N \bot}{\nonlineq \Gamma M N \bot}

@@

  \inferrule{\ctxwffjdg {\Gamma , b : Bool} {X(b)}}
        {\nonlineq
        {\Gamma, x_0 : X(false), x_1 : X(true)}
        {if\,false\,then\,x_0\,else\,x_1}
        {x_0}
        {X(false)}
      }

  \inferrule{\ctxwffjdg {\Gamma , b : Bool} {X(b)}}
        {\nonlineq
        {\Gamma, x_0 : X(false), x_1 : X(true)}
        {if\,true\,then\,x_0\,else\,x_1}
        {x_1}
        {X(true)}
      }

@@

  \inferrule
    {
      \nonlinterm {\Gamma} {M} {Y (nil)} \and
      \nonlinterm {\Gamma} {N}
      {\PiTyLimit {x} {X}
        {\PiTyLimit {xs} {\listTy{X}}
          {\PiTyLimit {ys} {Y(xs)} {Y(cons(x,xs))}}}}
    }
    {
      \nonlineq
      {\Gamma}
      {fold(M,N)(nil)}
      {y_{nil}}
      {Y(nil)}
    }

  \inferrule
    {
      \nonlinterm {\Gamma} {M} {Y (nil)} \and
      \nonlinterm {\Gamma} {N}
      {\PiTyLimit {x} {X}
        {\PiTyLimit {xs} {\listTy{X}}
          {\PiTyLimit {ys} {Y(xs)} {Y(cons(x,xs))}}}}
    }
    {
      \nonlineq
      {\Gamma, x : X, xs : \listTy{X}}
      {fold(M,N)(cons(x , xs))}
      {N(x)(xs)(fold(M,N)(xs))}
      {Y(cons(x , xs))}
    }

@@

\begin{figure}
  \begin{mathpar}
    \boxed{\Gamma ; \Delta \vdash e \equiv e' : A}

>>>>

@@

\begin{figure}
  \footnotesize
  \begin{mathpar}
    \boxed{
      \inferrule
      {\linctxwff \Gamma \Delta \and \linctxwffjdg \Gamma \A}
      {\linterm \Gamma \Delta {e} {A}}}

@@

\begin{figure}
  \begin{mathpar}
  \footnotesize
    \boxed{\inferrule{\ctxwffjdg \Gamma X}{\nonlinterm \Gamma M X}}

@@

    \inferrule
    {\nonlinterm \Gamma M \bot \and \ctxwffjdg \Gamma X}
    {\nonlinterm \Gamma {elim_{\bot}(X, M)} {X}}

@@

    \inferrule
    {
      \ctxwffjdg {\Gamma , b : Bool} {X(b)} \and
      \nonlinterm \Gamma {M_{0}} {X(false)} \and
      \nonlinterm \Gamma {M_{1}} {X(true)}
    }
    {\nonlinterm
        {\Gamma, b : Bool}
        {elim_{Bool}(X, M_0, M_1)(b)}
        {X(b)}
    }

@@

@@

\begin{figure}
  \begin{mathpar}
    \boxed{
      \inferrule
      {\nonlinterm \Gamma M X \and
       \nonlinterm \Gamma N X}
      {\nonlinterm \Gamma {M \equiv N} {X}}}

@@

  % \inferrule{\nonlinterm \Gamma M \bot \and \nonlinterm \Gamma N \bot}{\nonlineq \Gamma M N \bot}

@@

  \inferrule
  {
    \nonlinterm \Gamma {M_{0}} {X(false)} \and
    \nonlinterm \Gamma {M_{1}} {X(true)}
  }
  {\nonlineq
      {\Gamma}
      {elim_{Bool}(X, M_0,M_1)(false)}
      {M_0}
      {X(b)}
  }

  \inferrule
  {
    \nonlinterm \Gamma {M_{0}} {X(false)} \and
    \nonlinterm \Gamma {M_{1}} {X(true)}
  }
  {\nonlineq
      {\Gamma}
      {elim_{Bool}(X, M_0,M_1)(true)}
      {M_1}
      {X(b)}
  }

@@

@@

\begin{figure}
  \begin{mathpar}
    \boxed{
      \inferrule
      {\linterm \Gamma \Delta e A \and
       \linterm \Gamma \Delta e' A}
      {\Gamma ; \Delta \vdash e \equiv e' : A}}
